Detecting social information in a dense dataset of infants’ natural visual experience

### 2020-01-29 paper/cogsci/paper_jan28.Rmd
redo data sources, figures for paper

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
library(xtable)
theme_set(theme_few())
```

@@

```{r}
## Read in data 
### Load preprocessed and filtered detections
load('../../data_cogsci/openpose_detections_filtered_threekids_jan28.RData') #d_all
load('../../data_cogsci/openpose_detections_filtered_cropped_allthreekids_jan28.RData') # d_cropped
```

@@

```{r}
### Load file to filter flipped videos (when sam's mom was wearing camera; not egocentric)
right_side_up_file = "../../data_cogsci/video_right-side-up.csv"
right_side_up =read.csv(right_side_up_file)

# get INCORRECT videos
flipped_videos <- right_side_up %>%
  filter(right_side_up==1)

## load goal sample annotations
load('../../data_cogsci/ketan_gold_sample.RData')

## preprocess them
 ketan_gold_out <- ketan_gold %>%
   rowwise() %>%
   mutate(vid_name = str_split_fixed(vid_name,".mp4",2)[,1])%>%
   mutate(vid_name_short = str_split(vid_name,"[.]")[[1]][1]) %>%
   filter(!vid_name_short %in% flipped_videos$video) %>%
   mutate(face_openpose = as.logical(face_openpose), hand_openpose = as.logical(hand_openpose)) %>%
   rename(face_present_ketan = face_present, hand_present_ketan = hand_present)

# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

 ## evaluate detectors
 gold_sample <- ketan_gold_out %>%
  select(-vid_name) %>%
  rename(vid_name = vid_name_short) %>% 
  mutate(vid_name = as.factor(vid_name)) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))

@@

```{r} 
### Load turk hand annotations wtih all bounding boxes (multiple dets per frame)
turk_annotations_seg = "../../data_cogsci/turk_segmentations_hands_only_processed.csv" 
g_seg = read.csv(turk_annotations_seg) %>%
  select(-HITID, -HITTypeId, -WorkerID) %>%
  mutate(center_x = left + width/2, center_y = top + height/2)

child_hands <- g_seg %>%
  filter(label=="Child hand")

adult_hands <- g_seg %>%
  filter(label=="Adult hand")
```

```{r}
load('../../data_cogsci/child_adult_hand_annotations.RData')
# 
# hands_missed <- gold_sample %>%
#   select(-vid_name) %>%
#   rename(vid_name = vid_name_short) %>% 
#   mutate(vid_name = as.factor(vid_name)) %>%
#   left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
#   filter(!is.na(full_image_path)) %>%
#   filter(hand_eval_ketan == 'FN')

@@

```{r}
##
child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  # ggtitle('(A). Child hand density') +
  ylim(0,480) +
  xlim(0,640) +
  ylab('') +
  xlab('') +
  theme_few(base_size=12) +
  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse()
##
adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
  geom_point() + 
  stat_density_2d(aes(fill = ..level..), geom="polygon") +
  coord_fixed(ratio=1) +
  ylim(0,480) +
  xlim(0,640) +
  scale_y_reverse() +
  ylab('') +
  xlab('') +
  theme_few(base_size=12) +
    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) 
  # ggtitle('(B). Adult hand density') 
```

@@

```{r} 
load('../../data_cogsci/child_adult_hand_annotations.RData')

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs so they are counted
  filter(child_hand_seg==FALSE) %>%
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))

hand_performance_adults = return_prf_short(gold_sample_no_child_hands$hand_eval_adults)
```

@@

summary_by_age_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect) 
```

```{r FaceVsHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces (A), hands (B), and faces vs. hands (C) in the entire dataset and (D). when hand detections are restricted to the upper 60 percent of the field of view (B). Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range."}

faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10) + 
  ylab('Prop. Faces') + 
  # theme_few(base_size=16) +
  xlab('Age (months)') +
  ylim(0,.5) +
  theme(legend.position="none") +
  ggtitle('A.') +
  scale_colour_brewer(palette = "Dark2")

hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10) + 
  # theme_few(base_size=16) +
  ylab('Prop. Hands') + 
  xlab('Age (months)') +
  ylim(0,.5)+
  theme(legend.position="none") +
  ggtitle('B.') +
  scale_colour_brewer(palette = "Dark2")

face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10) + 
  # theme_few(base_size=16) +
  ylab('Prop. Faces - Hands') + 
  xlab('Age (months)') +
  ylim(-.3, .3) +
  theme(legend.position = "none") +
  ggtitle('C.') +
  scale_colour_brewer(palette = "Dark2")
###

faces_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10) + 
  ylab('Prop. Faces (Upper FOV)') + 
  # theme_few(base_size=16) +
  xlab('Age (months)') +
  ylim(0,.5) +
  theme(legend.position="none") +
  ggtitle('D.') +
  scale_colour_brewer(palette = "Dark2")

hands_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10) + 
  # theme_few(base_size=16) +
  ylab('Prop. Hands (Upper FOV)') + 
  xlab('Age (months)') +
  ylim(0,.5)+
  theme(legend.position="none") +
  ggtitle('E.') +
  scale_colour_brewer(palette = "Dark2")

face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10) + 
  # theme_few(base_size=16) +
  ylab('Prop. Faces - Hands (Upper FOV)') + 
  xlab('Age (months)') +
  ylim(-.3, .3) +
  theme(legend.position = "none") +
  ggtitle('F.')  +
  scale_colour_brewer(palette = "Dark2")

ggarrange(faces, hands, face_v_hand, faces_cropped, hands_cropped, face_v_hand_cropped, nrow=2)
```

@@

We thus re-analyzed the entire dataset while restricting our analysis to a smaller, upper portion of the frame comparable to the field of view used in @Fausey2016. To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame. This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.  Within this modified field of view, we still observed, on average, more hand detections than face detections.

However, we also still observed a moderate decrease in the proportion of faces vs. hands in view across age. To quantify this trend, we fit a generalized linear mixed model to the binned detection rates from this smaller field of field to estimate changes in the proportion of faces vs. hands over age. To better approximate @Fausey2016, we  restricted our analysis to the age range seen in @Fausey2016, excluding videos when children were over 24 months of age, and indeed found that the proportion of faces vs. hands declined modestly with age (see Table 1). Note that @Fausey2016 also included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.

```{r eval=FALSE}
summary_by_age_days_cropped_younger <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  filter(age_days < 730) %>% ## less than 24 months
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) %>%
  mutate(num_no_detect_faces = num_detect - num_faces, num_no_detect_hands = num_detect - num_hands)

summary_by_age_days_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
  mutate(num_no_detect_faces = num_detect - num_faces, num_no_detect_hands = num_detect - num_hands)

```{r eval=FALSE}
### Proportion faces vs. hands 
faces_model_full_age <- glmer(cbind(num_faces,num_no_detect_faces) ~ scale(age_days) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial")
# summary(faces_model_full_age)

hands_model_full_age <- glmer(cbind(num_hands,num_no_detect_hands) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
# summary(hands_model_full_age)

##
faces_model_younger <- glmer(cbind(num_faces,num_no_detect_faces) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped_younger, family = "binomial",  control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

hands_model_younger <- glmer(cbind(num_hands,num_no_detect_hands) ~ scale((age_days)) + (1 | child_id),  summary_by_age_days_cropped, family = "binomial", ,  control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

# faces_model_full_age_out <- summary(faces_model_full_age)
# xtable(faces_model_full_age_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.") 
```

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -1.55 & 0.03 & -52.47 & 0.000 \\ 
  scale(age\_days) & -0.13 & 0.00 & -261.57 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.} 
\end{table}

@@

```{r}
d_by_location_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
#

# d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location)
# levels(d_by_location_cropped$Location)

face_hand_by_location_cropped <- d_by_location_cropped %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected), num_detect = length(hand_detected))  %>%
  filter(num_detect > 12000) %>% ## 18000 frames = 10 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

hands_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="prop_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean))

faces_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="prop_faces") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean)) 
```

```{r DetByLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=4, fig.cap = "Proportion of faces (A),  hands (B), and faces vs. hands  (C) by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y). Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands. Each dot represents data from a week in which videos were filmed and are scaled by the number of frames (i.e., amount of video) in that datapoint."}

faces_loc = ggplot(faces_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(-.4,.4) +
  coord_flip() + 
  ylab('Proportion Faces')+
  xlab('')+
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none")

hands_loc = ggplot(hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(-.4,.4) +
  coord_flip() + 
  xlab('')+
  ylab('Proportion Hands') +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none")

ggarrange(faces_loc, hands_loc, nrow=2)
```
# General Discussion

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
library(xtable)
theme_set(theme_few())

# renv::init()
# https://rstudio.github.io/renv/articles/renv.html
```

@@

```{r}
## Read in data 
### Load preprocessed and filtered detections
load('../../data_cogsci/openpose_detections_filtered_2020-01-29.RData') # d_all
load('../../data_cogsci/openpose_detections_filtered_cropped_2020-01-29.RData') # d_cropped
```

@@

```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

@@

 ## load gold sample annotations
 load('../../data_cogsci/gold_sample_annotations_2020-01-29.RData') #d_all

 ## evaluate detectors
 gold_sample <- gold_sample %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_openpose), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_openpose))

@@

```{r}
### Examine gold sample performance by child hands
load('../../data_cogsci/child_adult_hand_annotations_by_frame.RData')
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_openpose))

hand_performance_adults = return_prf_short(gold_sample_no_child_hands$hand_eval_adults)

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load("../../data_cogsci/hand_annotations_2020-01-29.RData")

child_hands <- hand_annotations %>%
  filter(label=="Child hand")

adult_hands <- hand_annotations %>%
  filter(label=="Adult hand")

## plot centers of the bounding boxes made for child and adult hands
child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
  geom_point(alpha=.1) + 
  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
  coord_fixed(ratio=1) +
  # ggtitle('(A). Child hand density') +
  ylim(0,480) +
  xlim(0,640) +
  ylab('') +
  xlab('') +
  theme_few(base_size=12) +
  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse()
##
adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
  geom_point(alpha=.1) + 
  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
  coord_fixed(ratio=1) +
  ylim(0,480) +
  xlim(0,640) +
  scale_y_reverse() +
  ylab('') +
  xlab('') +
  theme_few(base_size=12) +
    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) 
  # ggtitle('(B). Adult hand density') 
```

@@

@@

summary_by_age_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_detected) / num_detect,  prop_hands = sum(hand_detected) / num_detect)

```{r}
wide_cropped <- summary_by_age_cropped %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "cropped",
         region = ifelse(region == "prop_faces","Face","Hands"))

wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces","Face","Hands"))

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_detect),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_detect)) + 
  geom_smooth(data = wide_cropped, aes(weight = num_detect),
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  theme(legend.position="bottom") +
  facet_grid(.~child_id) + 
  ggthemes::scale_color_solarized(name = "Detection") + 
  scale_size_continuous(name = "Detections (Log 10)")
```

@@

We thus re-analyzed the entire dataset while restricting our analysis to a smaller, upper portion of the frame comparable to the field of view used in @Fausey2016. To do so, we excluded hand detections that occurred in the bottom 40% of the frame, while retaining all hand detections that occurred in the top 60% of the frame. This coarse cropping of decreased the proportion of hand detections from `r round(mean(d_all$hand_openpose),2)`percent to `r round(mean(d_cropped$hand_detected),2)` percent, but only decreased face detections from `r round(mean(d_all$face_openpose),2)` to `r round(mean(d_cropped$face_detected),2)`.  Within this modified field of view, we still observed, on average, more hand detections than face detections'.

However, we also still observed a moderate decrease in the proportion of faces vs. hands in view across age. To quantify this trend, we fit a linear mixed model to the proportion of hands/faces observed, binned across the days in which the videos were filmed. T

 e foungain found that the proportion of faces vs. hands declined modestly with age (see Table 1). Note that @Fausey2016 also included data from very young infants (from 1-4 months of age), while here the youngest videos coming from S and A around 6 and 9 months of age, respectively.

```{r eval=FALSE}
summary_by_age_days_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(face_openpose), num_hands = sum(hand_detected), num_detect = length(face_openpose)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect)

summary_by_age_days_cropped_younger <- summary_by_age_days_cropped %>%
  filter(age_days < 730) ## less than 24 months
```
###
```{r}
library(lmerTest)
summary_by_age_days_cropped$age_scale <- scale(summary_by_age_days_cropped$age_days, scale = FALSE)[,1] / 30.3
# summary_by_age_days_cropped_younger$age_scale <- scale(summary_by_age_days_cropped_younger$age_days, scale = FALSE)[,1] / 30.3

faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_cropped))
```

```{r}
xtable(faces_model_full_age_out$coefficients, digits=c(2,2,2,2,3,3),"Model coefficients from a generalized linear mixed model predicting the proportion of faces seen by infants.")

xtable(hands_model_full_age_out$coefficients, digits=c(2,2,2,2,3,3),"Model coefficients from a generalized linear mixed model predicting the proportion of hands seen by infants.")
```

@@

```{r}
d_by_location_cropped <- d_cropped %>%
  replace_na(list(hand_detected = FALSE, face_detected = FALSE)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
# 
d_by_location_cropped$Location = droplevels(d_by_location_cropped$Location) # get rid of unused levels (more than 1 location)
# merge locations that seem similar
levels_to_modify = levels(d_by_location_cropped$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property
levels(d_by_location_cropped$Location) <- levels_to_modify

face_hand_by_location_cropped <- d_by_location_cropped %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected), num_detect = length(hand_detected))  %>%
  group_by(Location) %>%
  filter(num_detect > 12000) %>% ## 18000 frames = 10 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

hands_to_plot_cropped <- face_hand_by_location_cropped %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands") %>%
  mutate(region = "Hand") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  mutate(prop = prop_hands) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))

faces_to_plot_cropped <- face_hand_by_location_cropped %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces") %>%
  mutate(region = "Face") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  mutate(prop = prop_faces) %>%
  select(-prop_faces, -prop_hands) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter

both_to_plot <- faces_to_plot_cropped %>%
  full_join(hands_to_plot_cropped) %>%
  group_by(Location) %>%
  mutate(num_detect_location = sum(num_detect)) %>%
  ungroup() %>%
  mutate(Location = fct_reorder(Location, num_detect_location))
```

```{r DetByLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=4, fig.cap = "Proportion of faces and hands by location in which egocentric videos were filmed; data from individual children are plotted separately (location annotations were not available for Y). Data are only taken from the top 60 percent of the frames so as to minimize the contribution of children’s own hands. Each dot represents data from a week in which videos were filmed and are scaled by the number of frames in that datapoint."}

ggplot(both_to_plot, aes(x = Location, y = mean, col=region)) + 
  geom_point(aes(x=Location, y=prop, size=log10(num_detect)), alpha=.1, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  coord_flip() + 
  ylab('Proportion Detected')+
  xlab('')+
  ggthemes::scale_color_solarized(name = "Detection") + 
  theme(legend.position = "bottom") +
  facet_grid(.~child_id)  +
  scale_size_continuous(name = "Detections (Log 10)")
```

# General Discussion
